%!TEX root = ../report.tex
\documentclass[report.tex]{subfiles}
\begin{document}
    \chapter{Introduction}

    \begin{itemize}
        \item Brief description of SLAM in simple words.
    \end{itemize}
    
    
    \section{Motivation}
    \subsection{Topic of this RnD project}
    \begin{itemize}
        \item What is the topic to be covered?
        \item Where can it be used?
        \item What do you hope to achieve with this study?
    \end{itemize}

    \subsection{Relevance of the topic}
    \begin{itemize}
        \item Why choose this topic?
        \item Contextual Background: Provide a brief overview of the broader context within which your research is situated
        \item How can it benefit? real-world applications?
        \item Impact of the topic
        \item Address existing gap
        \item Why your research is timely and relevant in the current context
        \item Supporting Previous Findings: If your research aligns with or supports previous studies, discuss how it reinforces the existing knowledge base and provides additional evidence.
        \item Emerging Trends: Explain how your research aligns with or responds to emerging trends or developments in the field.
        \item Interdisciplinary Connections: If your research bridges multiple disciplines, highlight the importance of cross-disciplinary collaboration and how it enriches the understanding of the research problem.(the connection between traditional multi-view geometry of computer vision and the deep learning domain)
    \end{itemize}



    \section{Challenges and Difficulties}
    \subsection{Challenges}
    \begin{itemize}
        \item Existing problems. Acknowledge any challenges or limitations your research may face and how you plan to address them.
        \item What is required to solve the problem
        \item Data Availability and Collection: Discuss any potential challenges related to data availability, accessibility, or reliability. (dataset with GT object pose and GT trajectory information) (most papers deal only with qualitative comparisons than quantitative ones)
    \end{itemize}

    \subsection{Difficulties}
    \begin{itemize}
        \item Why is it difficult
        \item Potential obstacles
        \item occlusion of objects, dynamic objects, scale ambiguity in case of a monocular camera, data association problem, initialization problem.
    \end{itemize}



    \section{Problem Statement}
    \subsection{Aim of the Project}
    \begin{itemize}
        \item What are we going to do in this project
        \item Methodological Approach: Briefly mention the methodology or approach you will use to achieve the objectives.
        \item If any Novelty and Innovation
        \item Generalizability of your findings.
    \end{itemize}
    
    \subsection{Research Question}
    \begin{itemize}
        \item What are we issues are being addressed in this paper
        \item Unanswered questions that your research aims to address
        \item Formulate the research questions or hypotheses that will guide your investigation.
    \end{itemize}

\end{document}
