%!TEX root = ../report.tex
\documentclass[report.tex]{subfiles}
\begin{document}
    \chapter{State of the Art}

    %\section{....}
    %Use as many sections as you need in your related work to group content into logical groups

    %Don't forget to correctly cite your sources \cite{art1}.
    \section{2D SLAM}
    \begin{itemize}
        \item Explain what all sensors are being considered - 2D LIDAR and camera in case of semantics onto 2D plane. odometry from wheel encoders.
        \item What is 2D SLAM and where is it used?
    \end{itemize}

    \subsection{2D Mapping Methods}
    \begin{itemize}
        \item Different types of maps being created - topological, metric(occupancy grid), semantic, hybrid
        \item Different mapping methods - hector slam, cartographer, GMapping, KARTO-SLAM, Fast-SLAM, 2d semantic mapping methods
    \end{itemize}

    \subsection{2D Localization Methods}
    \begin{itemize}
        \item Different localization methods - variants of Kalman filter, variants of particle filter
        \item Usage of 2d semantic maps for localization
    \end{itemize}

    \section{3D SLAM}
    \begin{itemize}
        \item Which all sensors - RGBD camera, 3D LIDAR, Stereo camera. Not focusing on 3D SLAM with only 3D LIDAR.
        \item What is 2D SLAM and where is it used?
    \end{itemize}

    \subsection{3D Mapping Methods}
    \begin{itemize}
        \item Different types of maps being created - dense(entire point cloud, or 3d octomap), semi-dense(orb keypoints, important features only), sparse(semantics of object enclosed in shapes like cuboid, ellipsoid)
        \item Different mapping methods - kimera, orbslam, RTAB, LSD-SLAM, Cubeslam, EAO slam, PlanarSLAM, KinectFusion, ElasticFusion, DTAM
    \end{itemize}

    \subsection{3D Localization Methods}
    \begin{itemize}
        \item Visual localization - as in cuboidal slam, rat-slam 
        \item Keypoint based localization - as in orb slam
    \end{itemize}

    
    \section{Limitations of Previous Work}
    \begin{itemize}
        \item Why can't 2D SLAM be used in a dynamic environment?
        \item Problems with 2D localization.
        \item Size of the map to be stored.
        \item Time taken to create the map.
        \item Sensor inputs required for mapping.
        \item Time taken for localization.
        \item Online and offline map semantic processing.
        \item Computational power needed to process.
        \item Non-semantic maps cannot be used for semantic navigation. Cannot perform scene change detection.
    \end{itemize}


    
\end{document}
